Figure 6. Differential Protein expression

### 2022-10-11 reports/manuscript/Figure6.Rmd
add download link

#############
# LODA DATA #
#############
datasets_all_samples <- readRDS("../../results/03_normalize_data_output/datasets_all_samples.RDS")
Protein_V3 <- read_xlsx("../../data/Protein_norm_MFI_Bradley_et.al.xlsx")
cytokine_data <- read.csv("../../data/210125_Cytokines_visit3CVL.csv")
metadata <- read.csv("../../data/metadata.csv",row.names = 1, stringsAsFactors = F)

>>>>

prot_url <- "https://doi.org/10.1371/journal.ppat.1010494.s017"

############
# DOWNLOAD #
############
if(isFALSE(file.exists("../../data/Protein_norm_MFI.xlsx"))){download.file(prot_url, paste0("../../data/", "Protein_norm_MFI.xlsx"), method="auto")}

#############
# LODA DATA #
#############
datasets_all_samples <- readRDS("../../results/03_normalize_data_output/datasets_all_samples.RDS")
Protein_V3 <- read_xlsx("../../data/Protein_norm_MFI.xlsx", skip = 2) %>% rename(ID="Patient/Sample ID")
cytokine_data <- read.csv("../../data/210125_Cytokines_visit3CVL.csv")
metadata <- read.csv("../../data/metadata.csv",row.names = 1, stringsAsFactors = F)
